Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
renames confidenc.corr, and lift for the app. Also adds filters for pass/fail, low/high on the rhs

### CSPADE Algorithm
##TODO: FILTER FAILS AND LOW GRADE
Change name confidence corrected to confidence, confidence to confidence old, same for lift
```{r function clean SR}
# Transform rules from ruleInduction into a readable data frame
n_students <- length(unique(d_transactions$sequenceID))

@@

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence.corr = support / lhs.rhsCourse.support,
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students

      # TODO: coñpute rhs.support
      # lift.corr = confidence.corr / rhs.support

  ) %>%
  ungroup() %>%
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    )

@@

```
We apply cspade followed by rule induction
```{r cspade and rule induction, cache = F}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}

#Generating sequence rules
SR_taken   <- my_SR(data = sequences   )
SR_PF      <- my_SR(data = sequences_PF)
SR_HL      <- my_SR(data = sequences_HL)

SR_expanded_taken   <- my_SR(data = sequences_expanded   )
SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)
SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL,

>>>>

### CSPADE Algorithm
##TODO: FILTER FAILS AND LOW GRADE, paste item: e.g."COR1002_8"

```{r function clean SR}
# Transform rules from ruleInduction into a readable data frame
n_students <- length(unique(d_transactions$sequenceID))

@@

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    rename(confidence = "confidence.old", lift="lift.old")%>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = support / lhs.rhsCourse.support,
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students

      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support

  ) %>%
  ungroup() %>%
    mutate_at(
      c("support",
        "confidence","confidence.old", "lift.old"),
      funs(round(., 5))
    )

@@

```
We apply cspade followed by rule induction
```{r cspade and rule induction, cache = F}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}
# <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- 
# creating vector of fail course
course_id_fail <- d_transactions %>%
  filter(PF == "fail") %>%
  distinct(`item_PF`)

AR_HL <- my_apriori(transactions_HL,
                    appearance = list(both = course_id_low$`item_HL`))
# <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- 
#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )
#pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(`RHS Quality`=="fail")
#high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(`RHS Quality`=="low")

SR_expanded_taken   <- my_SR(data = sequences_expanded   )
SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% 
  filter(`RHS Quality`=="fail")
SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% 
  filter(`RHS Quality`=="low")
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL,
